### 2021-09-10 manuscript/field_data.tex

We applied the convolutional equivalent layer method to the aeromagnetic data of Carajás, 
northern Brazil.
The survey is composed of $131$ flight lines along north-south direction with line spacing of 
$\Delta y = 3,000$ m. 
Data were measured with spacing $\Delta x = 7.65$ m along lines, with an average distance 
to the ground of $900$ m.% (TEM QUE CHECAR)
The total number of observation points is $N = 6,081,345$. Figure \ref{fig:carajas_real_data_mag} 
shows the observed total-field anomaly data over the study area.

@@

As the study area is very large, the main magnetic field varies with position.
For this application, we set the main field direction as that of a mid location 
(latitude $-6.5^{\circ}$ and longitude $-50.75^{\circ}$) where the declination is $-19.86^{\circ}$ and
the inclination is $-7.4391^{\circ}$. Both values were calculated using the magnetic field calculator from NOAA
at 1st January, 2014 (epoch of the survey).
%
%\textbf{Alternative text} $\rightarrow$
%
%As the study area is very large, the main magnetic field varies with position.
%For this application, we set the main field direction as that of a mid location 
%(latitude $-6.5^{\circ}$ and longitude $-50.75^{\circ}$) where the declination is $-19.86^{\circ}$ 
%and inclination is $XXXXXX^{\circ}$ according to IGRF model at 1st January, 2014 (epoch of the survey).
%(É ESTRANHO CALCULAR A DECLINAÇÃO COM UM MODELO E A INCLINAÇÃO COM OUTRO)
%
%$\leftarrow$ \textbf{Alternative text}
%
We set the equivalent layer at $300$ meters above the ground ($600$ m below the data).
By applying our method to the interpolated regular grid 
(Figure \ref{fig:carajas_real_data_decimated_gridline}a), we obtain the  predicted data shown in 
Figure \ref{fig:carajas_gz_predito_mag_gridline}a and data residuals 
(Figure \ref{fig:carajas_gz_predito_mag_gridline}b) with mean $0.0762$ nT and the standard deviation 
$0.4886$ nT, revealing an acceptable data fitting.
Our method took $\approx 390.80$ seconds to converge at about $200$ iterations.% (TEM QUE CHECAR)
%
%POR QUE A CURVA DE CONVERGENCIA NÃO FOI MOSTRADA?
%
By applying our method to the decimated irregular grid 
(Figure \ref{fig:carajas_real_data_decimated_gridline}b), we obtain the predicted data shown in 
Figure \ref{fig:carajas_gz_predito_mag_decimated}a and data residuals 
(Figure \ref{fig:carajas_gz_predito_mag_decimated}b) with mean $0.0717$ nT and standard deviation 
$0.3144$ nT. In this case, our method took $\approx 385.56$ seconds 
to converge at about $200$ iterations (Figure \ref{fig:convergence_carajas_mag_decimated}).
%(TEM ALGO ESTRANHO AQUI. COMO QUE 2000 ITERAÇÕES FOI MAIS MAIS RÁPIDO DO QUE AS 200 ITERAÇÕES DO GRID INTERPOLADO?).
The convergence curve reveals a good convergence rate obtained with the decimated 
irregular grid. This result shows the robustness of our method in processing irregular grid.

>>>>

We applied the convolutional equivalent layer method to the aeromagnetic data of Carajás, 
northern Brazil.
The survey is composed of $131$ flight lines along north-south direction with line spacing of 
$\Delta y = 3,000$ m. 
Data were measured with spacing $\Delta x = 7.65$ m along lines, with an average distance 
to the ground of $900$ m. % (TEM QUE CHECAR)
The total number of observation points is $N = 6,081,345$. Figure \ref{fig:carajas_real_data_mag} 
shows the observed total-field anomaly data over the study area.

@@

As the study area is very large, the main magnetic field varies with position.
For this application, we set the main field direction as that of a mid location 
(latitude $-6.5^{\circ}$ and longitude $-50.75^{\circ}$) where the declination is $-19.86^{\circ}$ and
the inclination is $-7.4391^{\circ}$. Both values were calculated using the magnetic field calculator from NOAA
at 1st January, 2014 (epoch of the survey). 
%
%\textbf{Alternative text} $\rightarrow$
%
%As the study area is very large, the main magnetic field varies with position.
%For this application, we set the main field direction as that of a mid location 
%(latitude $-6.5^{\circ}$ and longitude $-50.75^{\circ}$) where the declination is $-19.86^{\circ}$ 
%and inclination is $XXXXXX^{\circ}$ according to IGRF model at 1st January, 2014 (epoch of the survey).
%(É ESTRANHO CALCULAR A DECLINAÇÃO COM UM MODELO E A INCLINAÇÃO COM OUTRO)
%
%$\leftarrow$ \textbf{Alternative text}
%
We set the equivalent layer at $300$ meters above the ground ($600$ m below the data).
By applying our method to the interpolated regular grid 
(Figure \ref{fig:carajas_real_data_decimated_gridline}a), we obtain the  predicted data shown in 
Figure \ref{fig:carajas_gz_predito_mag_gridline}a and data residuals 
(Figure \ref{fig:carajas_gz_predito_mag_gridline}b) with mean $0.0762$ nT and the standard deviation 
$0.4886$ nT, revealing an acceptable data fitting.
Our method took $\approx 390.80$ seconds to converge at about $200$ iterations. % (TEM QUE CHECAR)
%
%POR QUE A CURVA DE CONVERGENCIA NÃO FOI MOSTRADA?
%
By applying our method to the decimated irregular grid 
(Figure \ref{fig:carajas_real_data_decimated_gridline}b), we obtain the predicted data shown in 
Figure \ref{fig:carajas_gz_predito_mag_decimated}a and data residuals 
(Figure \ref{fig:carajas_gz_predito_mag_decimated}b) with mean $0.0717$ nT and standard deviation 
$0.3144$ nT. In this case, our method took $\approx 385.56$ seconds 
to converge at about $200$ iterations (Figure \ref{fig:convergence_carajas_mag_decimated}).
%(TEM ALGO ESTRANHO AQUI. COMO QUE 2000 ITERAÇÕES FOI MAIS MAIS RÁPIDO DO QUE AS 200 ITERAÇÕES DO GRID INTERPOLADO?).
The convergence curve reveals a good convergence rate obtained with the decimated 
irregular grid. This result shows the robustness of our method in processing irregular grid.
